---
title: "data-import1"
output: 
    slidy_presentation:
    theme: minty
  
---

## Inserting Data
Inserted data using read.csv of my shark attack data 
```{r}
SharkAttackdata <- read.csv("../data/SharkAttackdata.csv")
```

## Packages
I loaded the dplyr and ggplot2 packages. The dyplyr package helps to manipulate data whereas the ggplot2 helps to graph it and show it visually. 
```{r}
library(dplyr)
library(ggplot2)
library(prettydoc)

```

## New Data Tables Measuring Frequency
I created two new data tables in terms of their frequency for the collective 1960-2015 time frame. The first, is the water_area_frequency in which each water area frequency is counted for the collective time frame. The second, is the continent_freq table which each continent (or land mass) is counted for the collective time frame. 
```{r}
Water_area_freq <- count(SharkAttackdata, 'water_area')
```

```{r}
Continent_freq <- count(SharkAttackdata, 'continent')
```

## Bargraph with Continent and Frequency
I created a bar graph that gave the frequency of collective shark attacks between the years 1960 and 2015, by continent/land mass area. 
```{r}
ggplot(SharkAttackdata, aes(continent)) +
  geom_bar() +
   theme(legend.position = "bottom") +
    theme(legend.direction = "vertical") +
    theme(axis.text.x = element_text(angle = -90))
```



## Bargraph with Water Area and Frequency
I created a bar graph that gave the frequency of collective shark attacks between the years 1960 and 2015, by water area. 

```{r}
ggplot(SharkAttackdata, aes(water_area)) +
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 90))

```


```{r}
ggplot(SharkAttackdata, aes(year)) +
  geom_bar() + 
   theme(legend.position = "bottom") +
    theme(legend.direction = "vertical") +
    theme(axis.text.x = element_text(angle = 90))+
  scale_x_continuous( breaks=pretty(SharkAttackdata$year))
```


```{r}
USdata <- filter(SharkAttackdata, country == "USA")


ggplot(USdata, aes(state)) +
  geom_bar() + 
   theme(legend.position = "bottom") +
    theme(legend.direction = "vertical") +
    theme(axis.text.x = element_text(angle = 90))
```


```{r}

Floridaadata <- filter(USdata, state == "Florida")

ggplot(Floridaadata, aes(county)) +
  geom_bar() + 
   theme(legend.position = "bottom") +
    theme(legend.direction = "vertical") +
    theme(axis.text.x = element_text(angle = 90))

```


